Prediction maps of defoliation at trees

### 2021-12-06 analysis/eda.Rmd
[pre-commit.ci] auto fixes from pre-commit.com hooks
for more information, see https://pre-commit.ci

# load drake objects
loadd(
  vi_data, nri_data,
  bands_data, coords_vi_nri_clean,

  filter_values,
  filter_info_gain_nbins,

  trees_with_bands,
  trees_with_bands_no_buffer
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggpubr")
library("ggplot2")
library("knitr")
library("purrr")
library("sp")
library("raster")
library("fs")
library("patchwork")
library("here")
```

>>>>

# load drake objects
loadd(
  vi_data, nri_data,
  bands_data, coords_vi_nri_clean,
  filter_values,
  filter_info_gain_nbins,
  trees_with_bands,
  trees_with_bands_no_buffer
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggpubr")
library("ggplot2")
library("knitr")
library("purrr")
library("sp")
library("raster")
library("fs")
library("patchwork")
library("here")
```

### 2021-12-06 analysis/report-defoliation.Rmd
[pre-commit.ci] auto fixes from pre-commit.com hooks
for more information, see https://pre-commit.ci

# load drake objects
loadd(
  defoliation_raster,
  defoliation_raster_relative,
  defoliation_df,
  defoliation_df_relative,

  tune_xgboost_plan_project
)
```

@@

```{r echo = FALSE}
#system("rsync -rlptDivzog --chown=*:www-data --chmod=g+r,o+r /home/patrick/papers/2019-feature-selection/docs/figure/report-defoliation.Rmd/defol* patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/defoliation-maps/")
```

>>>>

# load drake objects
loadd(
  defoliation_raster,
  defoliation_raster_relative,
  defoliation_df,
  defoliation_df_relative,
  tune_xgboost_plan_project
)
```

@@

```{r echo = FALSE}
# system("rsync -rlptDivzog --chown=*:www-data --chmod=g+r,o+r /home/patrick/papers/2019-feature-selection/docs/figure/report-defoliation.Rmd/defol* patrick@jupiter.geogr.uni-jena.de:/home/www/life-healthy-forest/action-B1-spatial-mapping/defoliation-maps/")
```
